---
title: "Data Science Home Assignment"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

### Problem statement: 
### Use suitable data visualization tools (minimum 2) to compare data of 5 appropriately contrasting countries.<br>

Data set: Reference <http://www.data.un.org>. capital of GDP and GDP per capita.<br>

 Reading data set from the CSV file
```{r}
data <- read.csv("SYB63_230_202009_GDP and GDP Per Capita.csv")
```

Importing libraries needed
```{r}
library("highcharter")
library(dplyr) 
library(tidyverse)
library(ggplot2)
```

```{r}
data <- data[-c(1),]

names(data)[1] <- "Region/Country/Area No"
names(data)[2] <- "Region/Country/Area"
names(data)[3] <- "Year"
names(data)[4] <- "Series"
names(data)[5] <- "Value"
names(data)[6] <- "Footnotes"
names(data)[7] <- "Source"


data[,c(3,5)] <- sapply(data[,c(3,5)], as.numeric)
summary(data)
```

## GDP Growth of India
```{r}
#-----------------------------GDP Growth of INDIA--------------------------
highchart() %>% 
  hc_chart(type = "column") %>% 
  hc_xAxis(
    title = list(text = "Annual Year"),
    alternateGridColor = "#FDFFD5",
    plotLines = list(
      list(
        label = list(text = "This is a plotLine"),
        color = "#FF0000",
        width = 2,
        value = 5.5
      )
    )
  ) %>%
  hc_title(text = "Data of GDP Growth in India") %>% 
  hc_plotOptions(column = list(enableMouseTracking = TRUE)
  ) %>% 
  hc_add_series(name="1985",data=data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "India" & data$Year == "1985"]) %>%
  hc_add_series(name="1995",data=data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "India" & data$Year == "1995"]) %>%
  hc_add_series(name="2005",data=data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "India" & data$Year == "2005"]) %>%
  hc_add_series(name="2010",data=data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "India" & data$Year == "2010"]) %>%
  hc_add_series(name="2015",data=data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "India" & data$Year == "2015"]) %>%
  hc_add_series(name="2017",data=data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "India" & data$Year == "2017"]) %>%
  hc_add_series(name="2018",data=data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "India" & data$Year == "2018"]) 

```

## Data of GDP in 2018
```{r}
#---------------------Data of GDP in 2018--------------------------------------
pc <- mean(data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "China"]) 
print(pc)
highchart() %>% 
  hc_chart(type = "column") %>% 
  hc_xAxis(
    title = list(text = "5 appropriately contrasting countries"),
    alternateGridColor = "#FDFFD5",
    plotLines = list(
      list(
        label = list(text = "This is a plotLine"),
        color = "#FF0000",
        width = 2,
        value = 5.5
      )
    )
  ) %>%
  hc_title(text = "Data of GDP in 2018") %>% 
  hc_plotOptions(column = list(enableMouseTracking = TRUE)
  ) %>% 
  hc_add_series(name="India",data=tail(data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "India"], n=1))%>% 
  hc_add_series(name="Germany",data=tail(data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "Germany"], n=1))%>% 
  hc_add_series(name="Japan",data=tail(data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "Japan"], n=1))%>% 
  hc_add_series(name="China",data=tail(data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "China"], n=1))%>%
  hc_add_series(name="USA",data=tail(data$Value[data$Series == "GDP in current prices (millions of US dollars)" & data$`Region/Country/Area` == "United States of America"], n=1)) 

```

## Data of GDP Growth rate in 2018
```{r}
#--------------------------Data of GDP Growth rate in 2018----------------------------
pc <- mean(data$Value[data$Series == "GDP real rates of growth (percent)" & data$`Region/Country/Area` == "China"]) 
print(pc)
highchart() %>% 
  hc_chart(type = "column") %>% 
  hc_xAxis(
    title = list(text = "5 appropriately contrasting countries"),
    alternateGridColor = "#FDFFD5",
    plotLines = list(
      list(
        label = list(text = "This is a plotLine"),
        color = "#FF0000",
        width = 2,
        value = 5.5
      )
    )
  ) %>%
  hc_title(text = "Data of GDP Growth Rate in 2018") %>% 
  hc_plotOptions(column = list(enableMouseTracking = TRUE)
  ) %>%
  hc_add_series(name="Japan",data=tail(data$Value[data$Series == "GDP real rates of growth (percent)" & data$`Region/Country/Area` == "Japan"], n=1))%>% 
  hc_add_series(name="Germany",data=tail(data$Value[data$Series == "GDP real rates of growth (percent)" & data$`Region/Country/Area` == "Germany"], n=1))%>% 
  hc_add_series(name="USA",data=tail(data$Value[data$Series == "GDP real rates of growth (percent)" & data$`Region/Country/Area` == "United States of America"], n=1))%>% 
  hc_add_series(name="China",data=tail(data$Value[data$Series == "GDP real rates of growth (percent)" & data$`Region/Country/Area` == "China"], n=1))%>%
  hc_add_series(name="India",data=tail(data$Value[data$Series == "GDP real rates of growth (percent)" & data$`Region/Country/Area` == "India"], n=1)) 

```

## Data of GDP Per Capita in 2018
```{r}
#-------------------------Data of GDP Per Capita in 2018-----------------------------
pc <- mean(data$Value[data$Series == "GDP real rates of growth (percent)" & data$`Region/Country/Area` == "China"]) 
print(pc)
highchart() %>% 
  hc_chart(type = "column") %>% 
  hc_xAxis(
    title = list(text = "5 appropriately contrasting countries"),
    alternateGridColor = "#FDFFD5",
    plotLines = list(
      list(
        label = list(text = "This is a plotLine"),
        color = "#FF0000",
        width = 2,
        value = 5.5
      )
    )
  ) %>%
  hc_title(text = "Data of GDP Per Capita in 2018") %>% 
  hc_plotOptions(column = list(enableMouseTracking = TRUE)
  ) %>% 
  hc_add_series(name="India",data=tail(data$Value[data$Series == "GDP per capita (US dollars)" & data$`Region/Country/Area` == "India"], n=1))%>% 
  hc_add_series(name="China",data=tail(data$Value[data$Series == "GDP per capita (US dollars)" & data$`Region/Country/Area` == "China"], n=1))%>%
  hc_add_series(name="Japan",data=tail(data$Value[data$Series == "GDP per capita (US dollars)" & data$`Region/Country/Area` == "Japan"], n=1))%>% 
  hc_add_series(name="Germany",data=tail(data$Value[data$Series == "GDP per capita (US dollars)" & data$`Region/Country/Area` == "Germany"], n=1))%>% 
  hc_add_series(name="USA",data=tail(data$Value[data$Series == "GDP per capita (US dollars)" & data$`Region/Country/Area` == "United States of America"], n=1))

```

sub-setting data for line plots
```{r}
#sub-setting data for line plots
Region <- data$`Region/Country/Area`[data$`Region/Country/Area` == "India" | data$`Region/Country/Area` == "China" | data$`Region/Country/Area` == "Germany" | data$`Region/Country/Area` == "United States of America" | data$`Region/Country/Area` == "Japan"]
Year <-data$Year[data$`Region/Country/Area` == "India" | data$`Region/Country/Area` == "China" | data$`Region/Country/Area` == "Germany" | data$`Region/Country/Area` == "United States of America" | data$`Region/Country/Area` == "Japan"]
Series <-data$Series[data$`Region/Country/Area` == "India" | data$`Region/Country/Area` == "China" | data$`Region/Country/Area` == "Germany" | data$`Region/Country/Area` == "United States of America" | data$`Region/Country/Area` == "Japan"]
Value <-data$Value[data$`Region/Country/Area` == "India" | data$`Region/Country/Area` == "China" | data$`Region/Country/Area` == "Germany" | data$`Region/Country/Area` == "United States of America" | data$`Region/Country/Area` == "Japan"]
df <- data.frame(Region, Year, Series, Value)

```

## Data of GDP Growth Rate
```{r}
#---------------------------------Data of GDP Growth Rate------------------
growth <- subset(df, data$Series == "GDP real rates of growth (percent)")
ggplot(data=growth, aes(x=Year, y=Value, group=Region)) +
  geom_line(aes( color=Region), size = 1)+
  geom_point(aes(color = Region, size = 0.1))+
  theme(legend.position = "top")+
  labs(y = "Growth Rate", title = "GDP Growth Rate", subtitle = "from 1985 to 2018")
```

## GDP Per Capita
```{r}
#---------------GDP Per Capita-----------------------------------------
gdp_capita <- subset(df, data$Series == "GDP per capita (US dollars)")
ggplot(data=gdp_capita, aes(x=Year, y=Value, group=Region)) +
  geom_line(aes( color=Region), size = 1)+
  geom_point(aes(color = Region, size = 0.1))+
  theme(legend.position = "top")+
  labs(y = "GDP Per Capita", title = "GDP Per Capita (in US dollars)", subtitle = "from 1985 to 2018")

```

## GDP in constant 2010 Prices
```{r}
#--------------------GDP in constant 2010 Prices---------------------------------
gdp_2010 <- subset(df, data$Series == "GDP in constant 2010 prices (millions of US dollars)")
ggplot(data=gdp_2010, aes(x=Year, y=Value, group=Region)) +
  geom_line(aes( color=Region), size = 1)+
  geom_point(aes(color = Region, size = 0.1))+
  theme(legend.position = "top")+
  labs(y = "GDP in constant 2010 prices (millions of US dollars)", title = "GDP in constant 2010 prices (millions of US dollars)", subtitle = "from 1985 to 2018")
```

## Conclusion: 

Top-5 countries according to Gross Domestic Product<br>
China and India are growing at very fast rate<br>
Although USA, Japan, and Germany are currently growing at slow rate most of their GDP growth lies in 20th Century<br>
China has made very remarkable growth over small period of time<br>
Their is very greater need to increase GDP growth rate for India<br>
India is quite far from becoming a developed country. <br>
